Title

### 2018-09-20 thesis/paper/paper.tex
Typos

At the beginning the content of the Wikidata JSON-Dump, read via WDKT, is transformed into facts readable by VLog4J. These take the form of comma-separated value files, which are created for each predicate in Section \ref{subsec_representation}, denoted as "Facts" in the diagram.

At the same time the Inequaliy Helper, receiving the Facts from WDTK, creates all files necessary to establish inequality as described in Section \ref{sec_constraints_using_inequality}, based on which approach was chosen.

@@

Computing all violations based on the provided (inequality)-facts and violations rules is done per constraint type. All facts pertaining to the constraint, as well as the rules, are loaded into VLog, which creates an in-memory database from the provided .csv-files. Once this is done, the reasoning engine materializes all possible facts. Afterwards, all violations are extracted by querying the database for the queries described in Section \ref{subsec_task}.

@@

\subsection{Possible adaptations}
Since the problematic performance of \emph{item requires statement} and \emph{single value} are not visible in \emph{value requires statement} and \emph{single best value}, which are very similar in their rule modelling, a possible adaptation would be to not evaluate all constrained properties for these constraints in bulk but split them into smaller sets, evaluating each set individually to combat the problematic scaling of the require pattern. The precomputed datasets could be kept, meaning only the reasoning step would have to be repeated.

\subsection{Adaptations to VLog}

\subsubsection{Sorting facts for column-based storage}
VLog uses a column-based storage format where the first column is fully sorted and all following columns are sorted w.r.t. the preceding column. These columns are then run-length encoded. To minimize memory requirements and maximize access speed, predicates should be sorted in such a way that each entry has a smaller number of unique constants than the next entry.

@@

\subsubsection{Sorting conjunctions for left-to-right evaluation}
Conjunctions in VLog are evaluated from left to right, meaning the engine computes the matches of the first atom and, based on those findings, proceeds with the next atom. The rules as presented are not optimal regarding this process. Ideally, atoms should be sorted by the size of the intermediate results they incur.

>>>>

At the beginning the content of the Wikidata JSON-Dump, read via WDKT, is transformed into facts readable by VLog4J. These take the form of comma-separated value files, one for each predicate in Section \ref{subsec_representation}, denoted as "Facts" in the diagram.

At the same time the Inequaliy Helper, receiving the Facts from WDTK, creates all files necessary to establish inequality as described in Section \ref{sec_constraints_using_inequality}, based on which approach was chosen. These files are constraint type specific, whereas the "Facts" are not.

@@

Computing all violations based on the provided (inequality)-facts and violations rules is done per constraint type. All facts pertaining to the constraint, as well as the rules, are loaded into VLog, which creates an in-memory database from the provided .csv-files. For example, Once this is done, the reasoning engine materializes all possible facts. Afterwards, all violations are extracted by querying the database for the queries described in Section \ref{subsec_task}.

@@

\subsection{Adaptations to VLog - Sorting facts for column-based storage}
VLog uses a column-based storage format where the first column is fully sorted and all following columns are sorted w.r.t. the preceding column. These columns are then run-length encoded. To minimize memory requirements and maximize access speed, predicates should be sorted in such a way that each entry has a smaller number of unique constants than the next entry.

@@
